Stochastic Variance Reduced Policy Gradient

### 2018-01-24 svrpg.tex
Auto stash before merge of "master" and "origin/master"

We introduce two stopping condition: maximum number of sub-iterations and learning rate of Adam sub-iterations.
Adam update rule help to stabilize the gradient estimate. In fact, this method computes adaptive learning rates for each parameter that depends by history of gradients' variance.
In particular we use different Adam parameters: the first one for snapshot update and the second one for the sub-iterations update.
We stop if:

@@

\section{Experiments}
We design our experiments to investigate if:
\begin{enumerate}
\item Algorithm reaches high value of the reward function faster then GPOMDP.
\item Averagely SVRPG maintains the reward function more stable then GPOMDP.
\end{enumerate}

In order to analyze these topics, we evaluate the behavior of rewards function mediated by 10 runs for each experiment.

@@

In all the experiments we face with GPOMDP standard algorithm. GPOMDP uses a number of trajectories per batch that is equal to the number of trajectories used in SVRPG mini-batch size.
The neural network and the learning rate are the same for GPOMDP and SVRPG.
In SVRPG we implemented two different Adam parameters: the first one for Snapshot and the second one for sub-iterations.
We use the stopping condition defined in Section \ref{sec:stopping}.
We fixed the maximum number of trajectories that both the algorithms can use.

The neural networks is composed by one layer with 8 neurons for Cart-Pole environment and by two layers with 32x32 neurons for Swimmer and for Half Cheetah environments. In each experiment, the length of episodes is 500 steps.

@@

\section{Experimental Details}\label{app:proofs}
Environments of our experiments are:
\begin{enumerate}
	\item \emph{Cart-Pole Balancing} : 4-dimensional state space: cart position x, pole angle $\theta$, the cart velocity $\dot{x}$ , and the pole velocity $\dot{\theta}$; 1-dimensional action space: the horizontal force applied to the cart body. Reward function  is defined as $r(s, a) := 10 - (1 - cos(\theta)) - 10^{-5}\norm[] a^2$. Episodes terminates when $|x|>2.4$ or $|\theta|>0.2$ or the number of time step T is major than 100.
	\item \emph{Mujoco Swimmer}: 12-dimensional state space: 3 links velocities ($v_x$ and $v_y$ of center of masses) and 2 actuated joints angles. 2-dimensional action space: the two momentums applied on actuated joints.  Reward function is defined as $r(s, a) := v_x - 10^{-4}\norm[2] a^2$. Episodes terminates when the number of time step T is major than 500.
	\item \emph{Mujoco Half Cheetah}: 20-dimensional state space: 9 links and 6 actuated joints angles. 6-dimensional action space: the 6 momentums applied on actuated joints.  Reward function is defined as $r(s, a) := v_x - 0.05\norm[2] a^2$. Episodes terminates when the number of time step T is major than 500.
\end{enumerate}

>>>>

We introduce two stopping condition: maximum number of sub-iterations and learning rate of Adam sub-iterations.
Adam update rule help to stabilize the gradient estimate. In fact, this method computes adaptive learning rates for each parameter that depends on the history of the gradients' variance.
In particular we use different Adam parameters: the first one for snapshot updates and the second one for the sub-iterations updates.
We stop if:

@@

\section{Experiments}
We have designed our experiments to investigate whether:
\begin{enumerate}
\item The algorithm reaches high value of the reward function faster than GPOMDP.
\item Averagely SVRPG keep the reward function more stable than GPOMDP.
\end{enumerate}

In order to pursue the above mentioned objectives, we evaluate the behavior of the reward function averaged on 10 runs for each experiment.

@@

In all the experiments we compete with GPOMDP standard algorithm. GPOMDP uses a number of trajectories per batch that is equal to the number of trajectories used in SVRPG mini-batch size.
The neural network and the learning rate are the same for GPOMDP and SVRPG.
In SVRPG we used two different Adam parameters: the first one for Snapshot and the second one for sub-iterations.
We used the stopping condition defined in Section \ref{sec:stopping}.
We fixed the maximum number of trajectories that both the algorithms can use.

The neural networks is composed of one layer with 8 neurons for Cart-Pole environment and by two layers with 32x32 neurons for Swimmer and for Half Cheetah environments. In each experiment, the length of episodes is 500 steps.

@@

\section{Experimental Details}\label{app:proofs}
Setting specifications for all the used environments:
\begin{enumerate}
	\item \emph{Cart-Pole Balancing} : 4-dimensional state space: cart position x, pole angle $\theta$, cart velocity $\dot{x}$ and pole velocity $\dot{\theta}$; 1-dimensional action space: the horizontal force applied to the cart body. Reward function  is defined as $r(s, a) := 10 - (1 - cos(\theta)) - 10^{-5}\norm[] a^2$. The episodes terminates when $|x|>2.4$ or $|\theta|>0.2$ or the number of time steps T is greater than 100.
	\item \emph{Mujoco Swimmer}: 12-dimensional state space: 3 links velocities ($v_x$ and $v_y$ of center of masses) and 2 actuated joints angles. 2-dimensional action space: the two momentums applied on actuated joints.  The reward function is defined as $r(s, a) := v_x - 10^{-4}\norm[2] a^2$. The episodes terminates when the number of time steps T is greater than 500.
	\item \emph{Mujoco Half Cheetah}: 20-dimensional state space: 9 links and 6 actuated joints angles. 6-dimensional action space: the 6 momentums applied on actuated joints.  The reward function is defined as $r(s, a) := v_x - 0.05\norm[2] a^2$. The episodes terminates when the number of time steps T is greater than 500.
\end{enumerate}
